Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Spell check section on interacting system

    \subsection{Interacting hard sphere bosons}
        Moving to the full elliptical system for $\beta \neq 1$ and setting $a
        \neq 0$ we can write the trial wavefunction as
        \begin{align}
            \Psi_T(\vf{r})
            &=
            \Phi_T(\vf{r})
            J(\vf{r}),
        \end{align}
        where $\Phi_T(\vf{r})$ is the same Slater permanent as in
        \autoref{eq:initial_trial_wavefunction} and $J(\vf{r})$ is the
        \emph{Jastrow factor} given by
        \begin{align}
            J(\vf{r})
            &=
            \exp\para{
                \sum_{j < l}^N u(r_{jl})
            },
        \end{align}
        where
        \begin{align}
            u(r_{jk})
            = \ln\bigl[f(a, \vf{r}_j, \vf{r}_k)\bigr]
            \equiv u_{jk}
        \end{align}
        The drift force for particle $k$ in this system becomes
        \begin{align}
            \vf{F}_k(\vf{r})
            &=
            2\Biggl(
                \frac{\nabla_k\phi_k}{\phi_k}
                + \sum_{m \neq k}^N
                \nabla_k u_{km}
            \Biggr).
        \end{align}

        The Laplacian of particle $k$ divided by the trial wavefunction is
        \begin{widetext}
            \begin{align}
                \frac{\nabla_k^2\Psi_T(\vf{r})}{\Psi_T(\vf{r})}
                &=
                \frac{\nabla_k^2\phi_k}{\phi_k}
                + 2\frac{\nabla_k\phi_k}{\phi_k}
                \sum_{m \neq k}^N
                \frac{\Delta\vf{r}_{km}}{r_{km}}
                \dpd[]{u_{km}}{r_{km}}
                + \sum_{m\neq k}^N
                \para{
                    \frac{d - 1}{r_{km}}\dpd[]{u_{km}}{r_{km}}
                    + \dpd[2]{u_{km}}{r_{km}}
                }
                +
                \para{
                    \sum_{m \neq k}^N
                    \frac{\Delta\vf{r}_{km}}{r_{km}}
                    \dpd[]{u_{km}}{r_{km}}
                }^2,
                \label{eq:laplacian_full_system}
            \end{align}
        \end{widetext}
        where $\Delta \vf{r}_{km} = \vf{r}_k - \vf{r}_m$ and $d$ is the
        dimensionality. Evaluating the gradient and Laplacian of the single
        particle functions yields
        \begin{gather}
            \frac{\nabla_k\phi_k}{\phi_k}
            =
            -2\alpha
            (x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k),
            \\
            \frac{\nabla_k^2\phi_k}{\phi_k}
            =
            -2\alpha
            \big(
                d - 1 + \beta
            \bigr)
            + 4\alpha^2
            \bigl(
                x_k^2 + y_k^2 + \beta^2z_k^2
            \bigr).
        \end{gather}
        Repeating this for the correlation functions yields
        \begin{align}
            \dpd[]{u_{km}}{r_{km}}
            &=
            \frac{a}{r_{km}(r_{km} - a)},
            \\
            \dpd[2]{u_{km}}{r_{km}}
            &= \frac{a^2 - 2ar_{km}}{r_{km}^2(r_{km} - a)^2}.
        \end{align}
        The local energy is thus
        \begin{align}
            E_L(\vf{r})
            &=
            \sum_{k = 1}^N
            \brac{
                -\frac{\hbar^2}{2m}
                \frac{\nabla_k^2\Psi_T(\vf{r})}{\Psi_T(\vf{r})}
                + v(\vf{r}_k)
            },
        \end{align}
        where the Laplcian is given by \autoref{eq:laplacian_full_system}.  We
        will avoid writing out the full expression for the local energy for this
        system due to the size of the equation.

>>>>

    \subsection{Interacting hard sphere bosons}
        Moving to the full elliptical system for $\beta \neq 1$ and setting $a
        \neq 0$ we use the trial wavefunction from
        \autoref{eq:initial_trial_wavefunction}. We rewrite the Jastrow factor
        to
        \begin{align}
            J(\vf{r})
            &=
            \exp\para{
                \sum_{j < l}^N u(r_{jl})
            },
        \end{align}
        where
        \begin{align}
            u(r_{jk})
            = \ln\bigl[f(a, \vf{r}_j, \vf{r}_k)\bigr]
            \equiv u_{jk}
        \end{align}
        The drift force for particle $k$ in this system becomes
        \begin{align}
            \vf{F}_k(\vf{r})
            &=
            2\Biggl(
                \frac{\nabla_k\phi_k}{\phi_k}
                + \sum_{m \neq k}^N
                \nabla_k u_{km}
            \Biggr).
        \end{align}
        The Laplacian of particle $k$ divided by the trial wavefunction is then
        \begin{widetext}
            \begin{align}
                \frac{\nabla_k^2\Psi_T(\vf{r})}{\Psi_T(\vf{r})}
                &=
                \frac{\nabla_k^2\phi_k}{\phi_k}
                + 2\frac{\nabla_k\phi_k}{\phi_k}
                \sum_{m \neq k}^N
                \frac{\Delta\vf{r}_{km}}{r_{km}}
                \dpd[]{u_{km}}{r_{km}}
                + \sum_{m\neq k}^N
                \para{
                    \frac{d - 1}{r_{km}}\dpd[]{u_{km}}{r_{km}}
                    + \dpd[2]{u_{km}}{r_{km}}
                }
                +
                \para{
                    \sum_{m \neq k}^N
                    \frac{\Delta\vf{r}_{km}}{r_{km}}
                    \dpd[]{u_{km}}{r_{km}}
                }^2,
                \label{eq:laplacian_full_system}
            \end{align}
        \end{widetext}
        where $\Delta \vf{r}_{km} = \vf{r}_k - \vf{r}_m$ and $d$ is the
        dimensionality. Evaluating the gradient and the Laplacian of the single
        particle functions yields
        \begin{gather}
            \frac{\nabla_k\phi_k}{\phi_k}
            =
            -2\alpha
            (x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k),
            \\
            \frac{\nabla_k^2\phi_k}{\phi_k}
            =
            -2\alpha
            \big(
                d - 1 + \beta
            \bigr)
            + 4\alpha^2
            \bigl(
                x_k^2 + y_k^2 + \beta^2z_k^2
            \bigr).
        \end{gather}
        Repeating this for the correlation functions yields
        \begin{align}
            \dpd[]{u_{km}}{r_{km}}
            &=
            \frac{a}{r_{km}(r_{km} - a)},
            \\
            \dpd[2]{u_{km}}{r_{km}}
            &= \frac{a^2 - 2ar_{km}}{r_{km}^2(r_{km} - a)^2}.
        \end{align}
        The local energy is thus
        \begin{align}
            E_L(\vf{r})
            &=
            \sum_{k = 1}^N
            \brac{
                -\frac{\hbar^2}{2m}
                \frac{\nabla_k^2\Psi_T(\vf{r})}{\Psi_T(\vf{r})}
                + v(\vf{r}_k)
            },
        \end{align}
        where the Laplacian is given by \autoref{eq:laplacian_full_system}.  We
        will avoid writing out the full expression for the local energy for this
        system due to the size of the equation.
